\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{geometry}

\geometry{margin=1in}

\title{9-User Requirements for a Spotify-Like Application}
\date{}

\begin{document}

\maketitle

\section*{1. User Characteristics}
This section outlines the essential characteristics required for user accounts on the platform.

\begin{itemize}[leftmargin=*]
    \item \textbf{User ID and Username:} Each user must have a unique identifier and username to ensure distinct profiles and prevent duplication.
    \item \textbf{Age and Parental Controls:} The system will capture users’ ages and provide parental control options for younger users to monitor and manage accessible content.
    \item \textbf{Subscription and Payment Methods:} Users will have the option to select between free and premium subscriptions, with multiple flexible payment methods available.
    \item \textbf{Email and Contact Information:} Valid contact details, including email, are required for notifications and account recovery purposes.
    \item \textbf{Account Type:} Accounts will be categorized as either a regular User account or an Artist account, determining available features and functionalities.
\end{itemize}

\section*{2. Functional Requirements}
This section defines the key functionalities that the application must support.

\subsection*{2.1 User Management}
Functions related to managing user accounts and profiles.

\begin{itemize}[leftmargin=*]
    \item \textbf{Account Creation:} Users can register using email or phone, with an option for social media linked account sign-ins.
    \item \textbf{Profile Updates:} Users can update their profile information, including username, profile picture, and contact details.
    \item \textbf{Subscription Management:} Users can upgrade, downgrade, or cancel their subscriptions at any time, with corresponding feature adjustments.
    \item \textbf{Linked Accounts:} Users can link social media accounts to enhance connectivity and sharing options.
\end{itemize}

\subsection*{2.2 Music Streaming and Library Management}
Features related to music streaming and library organization.

\begin{itemize}[leftmargin=*]
    \item \textbf{Music Streaming:} The system shall provide free (with ads) and premium (ad-free) streaming options, with users controlling playback based on their subscription type.
    \item \textbf{Personalized Playlists:} Curated playlists tailored to user preferences and listening history will be offered (e.g., “Top Hits,” “Discover Weekly”).
    \item \textbf{Playlist Management:} Users can create, edit, and delete playlists, as well as add or remove songs.
    \item \textbf{Advanced Search:} Users can search for music by artist, title, genre, mood, and keywords for easy content location.
\end{itemize}

\subsection*{2.3 Social and Sharing Features}
Capabilities for users to interact and share their musical experiences.

\begin{itemize}[leftmargin=*]
    \item \textbf{Social Media Sharing:} Users can share playlists or songs on social media platforms through a visually appealing interface.
    \item \textbf{Follower and Following System:} Users can follow friends and artists to stay updated on new music and shared playlists.
    \item \textbf{Blending Feature:} Users can blend their music tastes with friends to explore common interests and discover new music.
    \item \textbf{Collaborative Playlists:} Users can co-create playlists with friends and listen together in real-time.
\end{itemize}

\section*{3. Non-Functional Requirements}
This section defines the performance criteria and constraints for the application.

\subsection*{3.1 Performance and Scalability}
Criteria for system performance and its ability to scale with user demand.

\begin{itemize}[leftmargin=*]
    \item \textbf{Load Time:} The system shall load songs within a maximum of 2 minutes to ensure a seamless user experience.
    \item \textbf{Search Query Performance:} The system shall efficiently handle a minimum of X concurrent search queries (replace X with a target number).
    \item \textbf{User Growth Management:} The system shall dynamically manage user growth to ensure consistent performance as the user base expands.
\end{itemize}

\subsection*{3.2 Usability and Accessibility}
Requirements ensuring the application is user-friendly and accessible to all.

\begin{itemize}[leftmargin=*]
    \item \textbf{User Interface Design:} The system shall feature an intuitive and user-friendly interface that facilitates easy navigation for all users.
    \item \textbf{Accessibility Standards:} The application shall comply with established accessibility standards, making it usable for individuals with disabilities and supporting multiple languages.
\end{itemize}

\subsection*{3.3 Security and Compliance}
Measures to protect user data and comply with legal requirements.

\begin{itemize}[leftmargin=*]
    \item \textbf{Data Encryption:} Sensitive user data shall be encrypted both in transit and at rest to protect against unauthorized access.
    \item \textbf{Multi-Factor Authentication:} The system shall implement multi-factor authentication to enhance security during user login.
    \item \textbf{Legal Compliance:} The system shall comply with applicable data protection laws and regulations, including automatic protection measures and secure data backup protocols.
\end{itemize}

\end{document}
